---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  fig.width = 12
)
```

# nutsr

An R package for austrian nuts regions, munacipies and districts.
Aimed to simplify your work with spatial variables in data analysis projects.

## Installation and setup

The package can be installed directly from github

```r
remotes::install_github('GregorDeCillia/nutsr')
```

Optional: Set up a cache with conversion rules and region polygons
This cache are used throughout the package.
Requires an active internet connection.
See below for data sources and usecases.
If this step is skipped, the cache will be populated on demand.

```{r}
library(nutsr)
nutsr_cache_dir('~/.cache/nutsr')
cache_conversion_rules()
cache_region_shapes()
```

## Conversion rules for regions

`nutsr` gives access to conversion rules for all nuts1, nuts2 and nuts3 regions
as well as munacipies (`iso3`) and districts (`iso5`).
This data has been collected via the [`{STATcubeR}`] package.
Conversion rules are data frames with three columns: code, parent and name.
They provide a custom `summary()` method.

```{r}
head(nuts2(), 4)

summary(nuts1())

summary(nuts2())

summary(nuts3())

summary(iso1())

summary(iso3())

summary(iso5())
```

## Utility functions for data analysis

`nutsr` provides several utility functions to make data analysis easier.
All these utility functions make use of the tables above.

#### Convert codes to labels or vice versa

```{r}
region_labels(c('AT1', 'AT11', 'AT111', '10101'))

region_codes(c("Ostösterreich", "Burgenland", "Mittelburgenland", "Eisenstadt"))
region_codes("Burgenland", prefer = "iso")
```

#### Get information about hierarchies

```{r}
region_parents(c('AT1', 'AT11', 'AT111', '10101'))

region_levels(c('AT1', 'AT11', 'AT111', '1', '101', '10101'))
```

## Data visualization

Visualize regional data with `nuts_map()`.
This will create a [`{leaflet}`] map for the regions.

```{r, include = FALSE}
library(sf)
library(dplyr)
```


```{r nuts3_plot}
library(sf)
y <- iso3_pop()
nuts_map(y)
library(dplyr)
iso5_pop() %>% 
  filter(substr(iso, 1, 1) == 9) %>% 
  nuts_map(overlay_nuts2 = FALSE)
```

## Similar projects

The [`{eurostat}`] package contains information about nuts1, nuts2 and nuts3
regions for all EU27 countries, including austria.

```r
?eurostat::add_nuts_level
?eurostat::recode_to_nuts_2016
?eurostat::get_eurostat_geospatial
```

[`{leaflet}`]: https://rstudio.github.io/leaflet/
[`{STATcubeR}`]: https://statistikat.github.io/STATcubeR/
[`{eurostat}`]: https://ropengov.github.io/eurostat/
