---
title: "Data visualization with nutsr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data visualization with nutsr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`{nutsr}` provides functions to visualize spatial data.
This article showcases currently implemented methods as well as some prototypes for future visualization.

## Maps

`nuts_map()` creates maps of regions using the `{leaflet}` package.
The input dataset should contain region codes that are compatible with `{nutsr}`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>", 
  out.width = "100%",
  fig.align = 'center'
)
library(nutsr)
library(sf)
library(dplyr)
library(highcharter)
```

```{r, eval = TRUE}
library(nutsr)
library(sf)
library(dplyr)

y <- iso3_pop()
nuts_map(y)

iso5_pop() %>% 
  filter(substr(iso, 1, 1) == 9) %>% 
  nuts_map(overlay_nuts2 = FALSE)
```

## Drilldown

`nuts_drilldown()` allows you to create graphs similar to https://www.highcharts.com/demo/column-drilldown
based on iso5 data. Regions can be expanded by clicking on the bars.
It is planned to also add support for iso3 data in the future.

```{r, out.height='500px'}
nuts_drilldown(iso5_pop(), title = "Population of ${name}", 
               value_label = "population")
```

To use this function with `{STATcubeR}` datasets, it is easiest to
use the `raw` parameter of the `$tabulate()` method.

```{r, eval = TRUE}
x <- STATcubeR::od_table('OGD_gem_basis_quer1_GemHH_BQ_1')
y <- x$tabulate("Commune", "Ordinary expenditures", raw = TRUE)
y <- y[y[[1]] %in% iso5()$code, ]
nuts_drilldown(y, title = "ordinary expenditures in ${name}",
               value_label = "expenditures")
```

## Scatter

```{r, out.height='300px'}
readRDS('graphs/by_age.rds')
```

## Timeseries

```{r, out.height='300px'}
readRDS('graphs/ts_to_bar.rds')
```

[sunburst diagram]: https://www.highcharts.com/demo/sunburst
